---
title: Multiomics reveals persistence of obesity-associated adipose tissue immune
  cell phenotypes during weight loss and subsequent weight regain
author: "Matthew A. Cottam"
subtitle: "Figure 1"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    theme: journal
    fig_caption: yes
    toc: yes
---

# Setup

```{r prep, warning=FALSE, message=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(ggsci)
library(Seurat)
library(RColorBrewer)
library(ggridges)
library(viridis)

#Weight cycling group colors
wccols <- c("Lean" = "#878787", 
            "Obese" = "#518db6",
            "WL" = "#94cc73",
            "WC" = "#e96b53")
```

# Figure 1

Figure one introduces our weight cycling model and the resulting phenotype from mice across multiple previous studies to show the robustness of the model and resulting glucose impairment.

```{r Fig1Setup}
#Import Body Mass Data
bodymass <- read.csv("../Inputs/Fig1/WC-Grouped_BodyMass.csv")
bodymass <- reshape2::melt(bodymass, id.vars=c("MouseID","Group","Study"), measure.vars=colnames(bodymass)[4:31], variable.name="Week", value.name="Bodymass")
bodymass$Group <- factor(bodymass$Group, levels = c("Lean","Obese","WL","WC"))
bodymass <- subset(bodymass, MouseID!="1852" & MouseID!="1853" & MouseID!="1854" & MouseID!="1855" &
                             MouseID!="1860" & MouseID!="1861" & MouseID!="1863" & MouseID!="1867") #These animals are part of a separate study model and are removed.
bodymass <- subset(bodymass, Bodymass!="NA")
#Body Mass Error Calculation
bodymass_sem <- bodymass %>%
  group_by(Group, Week) %>%
  summarize(mean = mean(Bodymass), sd = sd(Bodymass))
bodymass_n <- bodymass %>% dplyr::count(Group, Week)
bodymass_sem$n <- bodymass_n$n
bodymass_sem <- bodymass_sem %>% mutate(sem = sd/sqrt(n))
colnames(bodymass_sem) = c("Group","Week","Bodymass","sd","n","sem")

#Import Food Intake
foodintake <- read.csv("../Inputs/Fig1/WC-Grouped_FoodIntake.csv") #Samples from MC2 did not have food intake measured.
foodintake <- foodintake[,-(31:52)] #Extra empty columns in the csv?
foodintake <- reshape2::melt(foodintake, id.vars=c("MouseID","Group","Study"), measure.vars=colnames(foodintake)[4:30], variable.name="Week", value.name="foodintake")
colnames(foodintake) <- c("Mouse","Group","Study","Week","FoodIntake")
foodintake$Group <- factor(foodintake$Group, levels = c("Lean","Obese","WL","WC"))
foodintake <- subset(foodintake, Mouse!="1852" & Mouse!="1853" & Mouse!="1854" & Mouse!="1855" &
                             Mouse!="1860" & Mouse!="1861" & Mouse!="1863" & Mouse!="1867")
foodintake <- subset(foodintake, FoodIntake!="NA")

#Food Intake Error Calculation
foodintake_sem <- foodintake %>%
  group_by(Group, Week) %>%
  summarize(mean = mean(FoodIntake), sd = sd(FoodIntake))
foodintake_n <- foodintake %>% dplyr::count(Group, Week)
foodintake_sem$n <- foodintake_n$n
foodintake_sem <- foodintake_sem %>% mutate(sem = sd/sqrt(n))
colnames(foodintake_sem) = c("Group","Week","FoodIntake","sd","n","sem")

#Import Cumulative Food Intake
CumulativeFI <- read.csv("../Inputs/Fig1/WC-Grouped_CumulativeFoodIntake.csv")
CumulativeFI <- reshape2::melt(CumulativeFI, id.vars=c("MouseID","Group","Study"), measure.vars=colnames(CumulativeFI)[5:32], variable.name="Week", value.name="c_foodintake")
colnames(CumulativeFI) <- c("Mouse","Group","Study","Week","C_FoodIntake")
CumulativeFI$Group <- factor(CumulativeFI$Group, levels = c("Lean","Obese","WL","WC"))
CumulativeFI <- subset(CumulativeFI, Mouse!="1852" & Mouse!="1853" & Mouse!="1854" & Mouse!="1855" &
                             Mouse!="1860" & Mouse!="1861" & Mouse!="1863" & Mouse!="1867")
CumulativeFI <- subset(CumulativeFI, C_FoodIntake!="NA")

#Food Intake Error Calculation
CumulativeFI_sem <- CumulativeFI %>%
  group_by(Group, Week) %>%
  summarize(mean = mean(C_FoodIntake), sd = sd(C_FoodIntake))
CumulativeFI_n <- CumulativeFI %>% dplyr::count(Group, Week)
CumulativeFI_sem$n <- CumulativeFI_n$n
CumulativeFI_sem <- CumulativeFI_sem %>% mutate(sem = sd/sqrt(n))
colnames(CumulativeFI_sem) = c("Group","Week","C_FoodIntake","sd","n","sem")

#Import Body Comp (NMR)
bodycomp <- read.csv("../Inputs/Fig1/WC-Grouped_BodyComp.csv")
bodycomp <- reshape2::melt(bodycomp, id.vars=c("MouseID","Group","Study"), measure.vars=colnames(bodycomp)[5:6], variable.name="Source", value.name="Mass")
bodycomp <- subset(bodycomp, MouseID!="1852" & MouseID!="1853" & MouseID!="1854" & MouseID!="1855" &
                             MouseID!="1860" & MouseID!="1861" & MouseID!="1863" & MouseID!="1867" & 
                             Mass!="NA")
bodycomp$Group <- factor(bodycomp$Group, levels = c("Lean","Obese","WL","WC"))
#For HLC90 and HLC56, the body comp was found to be broken and measuring inaccurately. The other studies were done in the VMMPC, where the machine is better maintained.
bodycomp <- subset(bodycomp, Study!= "HLC56" & Study != "HLC90")

#Body Comp Error Calculation
bodycomp_sem <- bodycomp %>%
  group_by(Group, Source) %>%
  summarize(mean = mean(Mass), sd = sd(Mass))
bodycomp_n <- bodycomp %>% dplyr::count(Group, Source)
bodycomp_sem$n <- bodycomp_n$n
bodycomp_sem <- bodycomp_sem %>% mutate(sem = sd/sqrt(n))
colnames(bodycomp_sem) = c("Group","Source","Mass","sd","n","sem")

#Import ipGTT
gtt <- read.csv("../Inputs/Fig1/WC-Grouped_ipGTT.csv")
gtt <- gtt[,-12] #Most studies only went out to 120 or 150 min, so removing the 180min time point.
gtt <- reshape2::melt(gtt, id.vars=c("MouseID","Group","Study"), measure.vars=colnames(gtt)[4:11], variable.name="Time", value.name="PlasmaGlucose")
colnames(gtt) <- c("Mouse","Group","Study","Time","PlasmaGlucose")
gtt$Group <- factor(gtt$Group, levels = c("Lean","Obese","WL","WC"))
gtt$Time <- ifelse(gtt$Time == "X0",0,
                   ifelse(gtt$Time == "X15", 15,
                          ifelse(gtt$Time == "X30",30,
                                 ifelse(gtt$Time == "X45",45,
                                        ifelse(gtt$Time == "X60",60,
                                               ifelse(gtt$Time == "X90",90,
                                                      ifelse(gtt$Time == "X120", 120,
                                                             ifelse(gtt$Time == "X150", 150, NA)))))))) #This is definitely not the most efficient way to do this, but it works and is robust.
gtt <- subset(gtt, Mouse!="1852" & Mouse!="1853" & Mouse!="1854" & Mouse!="1855" &
                             Mouse!="1860" & Mouse!="1861" & Mouse!="1863" & Mouse!="1867")
gtt <- subset(gtt, PlasmaGlucose!="NA")

#ipGTT Error Calculation
gtt_sem <- gtt %>%
  group_by(Group, Time) %>%
  summarize(mean = mean(PlasmaGlucose), sd = sd(PlasmaGlucose))
gtt_n <- gtt %>% dplyr::count(Group, Time)
gtt_sem$n <- gtt_n$n
gtt_sem <- gtt_sem %>% mutate(sem = sd/sqrt(n))
colnames(gtt_sem) = c("Group","Time","PlasmaGlucose","sd","n","sem")

#Import Sac Mass
tissuemass <- read.csv("../Inputs/Fig1/WC-Grouped_TissueMass.csv") #Depending on study constraints, we expect many NA values here.
tissuemass <- reshape2::melt(tissuemass, id.vars=c("MouseID","Group","Study"), measure.vars=colnames(tissuemass)[4:6], variable.name="Tissue", value.name="Mass")
tissuemass <- subset(tissuemass, MouseID!="1852" & MouseID!="1853" & MouseID!="1854" & MouseID!="1855" &
                             MouseID!="1860" & MouseID!="1861" & MouseID!="1863" & MouseID!="1867" & 
                             Mass!="NA")
tissuemass <- subset(tissuemass, MouseID!="1387" & MouseID!="1388" & MouseID!="1389" & MouseID!="1390") #Liver mass for these mice was not recorded for total tissue weight (just a small piece for protein measurement). I've removed them from all tissue weights altogether to avoid any confusion.
tissuemass$Group <- factor(tissuemass$Group, levels = c("Lean","Obese","WL","WC"))

#Sac Mass Error Calculation
tissuemass_sem <- tissuemass %>%
  group_by(Group, Tissue) %>%
  summarize(mean = mean(Mass), sd = sd(Mass))
tissuemass_n <- tissuemass %>% dplyr::count(Group, Tissue)
tissuemass_sem$n <- tissuemass_n$n
tissuemass_sem <- tissuemass_sem %>% mutate(sem = sd/sqrt(n))
colnames(tissuemass_sem) = c("Group","Tissue","Mass","sd","n","sem")

#Calculate the AUC
gtt <- gtt %>% arrange(Mouse)
auc <- distinct(gtt[,1:2])
AUC=NULL
for (mouse in unique(gtt$Mouse)){
AUC <- rbind(AUC,(sum(diff(subset(gtt, Mouse==mouse)$Time)*(head(subset(gtt, Mouse==mouse)$PlasmaGlucose,-1)+tail(subset(gtt, Mouse==mouse)$PlasmaGlucose,-1)))/2))
}
auc$AUC <- AUC[,1]
auc$Group <- factor(auc$Group, levels=c("Lean","Obese","WL","WC"))

#Error for AUC
auc_sem <- auc %>%
  group_by(Group) %>%
  summarize(mean = mean(AUC), sd = sd(AUC))
auc_n <- auc %>% dplyr::count(Group)
auc_sem$n <- auc_n$n
auc_sem <- auc_sem %>% mutate(sem = sd/sqrt(n))
colnames(auc_sem) = c("Group","AUC","sd","n","sem")

#Figure options
wccols = c("#878787", "#518db6","#94cc73","#e96b53")
```

## Figure 1A
Figure 1 panel A is just a summary schematic of our WC model.

## Figure 1B

```{r Fig1b, fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
ggplot(bodymass, aes(x=as.numeric(Week)-1, y=Bodymass, color=Group)) + 
  geom_point(stat="summary", size=2) + 
  geom_line(stat="summary", size=1) +
  geom_errorbar(data=bodymass_sem, aes(ymin=Bodymass-sem, ymax=Bodymass+sem), width=0.5) + 
  theme_pubr(base_size=12) +
  NoLegend() + 
  labs(x="Weeks on Diet", y="Body Mass (g)") +
  scale_x_continuous(breaks=seq(from=0, to=27, by=3)) + 
  ylim(0,60) + 
  scale_color_manual(values=wccols) +
  geom_vline(xintercept = c(9,18), linetype="dashed")

#ANOVA
compare_means(Bodymass ~ Group, data = bodymass, method="anova") #Across all weeks 
compare_means(Bodymass ~ Group, data = bodymass, group.by="Week",method="anova") #By week

#T.tests with Bonferroni correction for multiple comparisons
compare_means(Bodymass ~ Group, data = bodymass, group.by="Week", method="t.test", p.adjust.method="bonferroni")

```

## Figure 1C

```{r Fig1c, fig.height=3, fig.width=4, message=FALSE}
ggplot(foodintake, aes(x=as.numeric(Week), y=FoodIntake, color=Group)) + 
  geom_point(stat="summary", size=2) + 
  geom_line(stat="summary", size=1) +
  geom_errorbar(data=foodintake_sem, aes(ymin=FoodIntake-sem, ymax=FoodIntake+sem), width=0.5) + 
  theme_pubr(base_size=12) +
  NoLegend() + 
  labs(x="Weeks on Diet", y="Food Intake \n (Avrg kcal/day/mouse)") +
  scale_x_continuous(breaks=seq(from=0, to=27, by=3)) + 
  ylim(0,25) + 
  scale_color_manual(values=wccols) +
  geom_vline(xintercept = c(9,18), linetype="dashed")

#ANOVA
compare_means(FoodIntake ~ Group, data = foodintake, method="anova") #Across all weeks 
compare_means(FoodIntake ~ Group, data = foodintake, group.by="Week",method="anova") #By week

#T.tests with Bonferroni correction for multiple comparisons
compare_means(FoodIntake ~ Group, data = foodintake, group.by="Week", method="t.test", p.adjust.method="bonferroni")
```

## Figure 1D

```{r Fig1d, fig.height=3, fig.width=4, message=FALSE}
ggplot(CumulativeFI, aes(x=as.numeric(Week)-1, y=C_FoodIntake, color=Group)) + 
  geom_point(stat="summary", size=2) + 
  geom_line(data=subset(CumulativeFI, Week=="wk0" | Week=="wk9"|Week=="wk18"|Week=="wk27"), aes(x=as.numeric(Week)-1, y=C_FoodIntake, color=Group),stat="summary", size=1) +
  geom_errorbar(data=CumulativeFI_sem, aes(ymin=C_FoodIntake-sem, ymax=C_FoodIntake+sem), width=0.5) + 
  theme_pubr(base_size=12) +
  NoLegend() + 
  labs(x="Weeks on Diet", y="Cumulative Food Intake \n (kcal/mouse)") +
  scale_x_continuous(breaks=seq(from=0, to=27, by=3)) + 
  ylim(0,4000) + 
  scale_color_manual(values=wccols) +
  geom_vline(xintercept = c(9,18), linetype="dashed")


#Calculate slope for each interval
slopeFI <- CumulativeFI[which(CumulativeFI$Week %in% c("wk0","wk9","wk18","wk27")),] %>% group_by(Group, Week) %>%
  summarize(mean = mean(C_FoodIntake)) %>% mutate(Week=as.numeric(Week)-1)



#Model splitting by group; each model is for a 9wk interval
model1 <- dlply(slopeFI[slopeFI$Week %in% c(0,9),], c("Group"), function(df) 
  lm(mean ~ Week, data = df))

model2 <- dlply(slopeFI[slopeFI$Week %in% c(9,18),], c("Group"), function(df) 
  lm(mean ~ Week, data = df))

model3 <- dlply(slopeFI[slopeFI$Week %in% c(18,27),], c("Group"), function(df) 
  lm(mean ~ Week, data = df))

# Apply coef to each model and return a data frame
ldply(model1, coef)
ldply(model2, coef)
ldply(model3, coef)

```

## Figure 1E

```{r Fig1e, fig.height=3, fig.width=4}
ggplot(subset(bodycomp,Source=="Lean_g"), aes(x=Group, y=Mass, fill=Group)) + 
  geom_bar(stat="summary", color="black", width=0.8) + 
  geom_errorbar(data=subset(bodycomp_sem, Source=="Lean_g"), aes(ymin=Mass-sem, ymax=Mass+sem), width=0.25) + 
  geom_jitter(size=0.5, width=0.3, alpha=0.7) + 
  theme_pubr(base_size=11) +
  NoLegend() + 
  labs(x="", y="Lean Mass (g)") + 
  scale_fill_manual(values=wccols) +
  theme(aspect.ratio = 1.5, axis.text.x = element_text(angle=45, hjust=1, vjust=0.98)) 

ggplot(subset(bodycomp,Source=="Fat_g"), aes(x=Group, y=Mass, fill=Group)) + 
  geom_bar(stat="summary", color="black", width=0.8) + 
  geom_errorbar(data=subset(bodycomp_sem, Source=="Fat_g"), aes(ymin=Mass-sem, ymax=Mass+sem), width=0.25) + 
  geom_jitter(size=0.5, width=0.3, alpha=0.7) + 
  theme_pubr(base_size=11) +
  NoLegend() + 
  labs(x="", y="Fat Mass (g)") + 
  scale_fill_manual(values=wccols) +
  theme(aspect.ratio = 1.5, axis.text.x = element_text(angle=45, hjust=1, vjust=0.98)) 

### T.test with Bonferroni correction for multiple comparisons
compare_means(Mass ~ Group, data = subset(bodycomp,Source=="Lean_g"), method="t.test", p.adjust.method = "bonferroni")# Lean Mass

compare_means(Mass ~ Group, data = subset(bodycomp,Source=="Fat_g"), method="t.test", p.adjust.method = "bonferroni")# Fat Mass
```

## Figure 1F

```{r Fig1f, fig.height=3, fig.width=4}
#GTT -----
ggplot(gtt_sem, aes(x=Time, y=PlasmaGlucose, color=Group)) + 
  geom_point(stat="summary", size=2) + 
  geom_line(stat="summary", size=1) +
  geom_errorbar(data=gtt_sem, aes(ymin=PlasmaGlucose-sem, ymax=PlasmaGlucose+sem), width=0.25) + 
  theme_pubr(base_size=12) +
  NoLegend() + 
  labs(x="Time (min)", y="Plasma Glucose (mg/dL)") +
  scale_x_continuous(breaks=seq(from=0, to=150, by=30)) + 
  ylim(0,500) + 
  scale_color_manual(values=wccols) 

#ANOVA
compare_means(PlasmaGlucose ~ Group, data = gtt, method="anova") #Across all timepoints
compare_means(PlasmaGlucose ~ Group, data = gtt, group.by="Time",method="anova") #By time

#T.tests with Bonferroni correction for multiple comparisons
compare_means(PlasmaGlucose ~ Group, data = gtt, group.by="Time", method="t.test", p.adjust.method="bonferroni")

#To copy Legend only
ggplot(gtt_sem, aes(x=Time, y=PlasmaGlucose, color=Group)) + 
  geom_point(stat="summary", size=2) + 
  geom_line(stat="summary", size=1) +
  geom_errorbar(data=gtt_sem, aes(ymin=PlasmaGlucose-sem, ymax=PlasmaGlucose+sem), width=0.25) + 
  theme_classic(base_size=12) +
  labs(x="Time (min)", y="Plasma Glucose (mg/dL)") +
  scale_x_continuous(breaks=seq(from=0, to=150, by=30)) + 
  ylim(0,500) + 
  scale_color_manual(values=wccols) 
#AUC------
ggplot(auc_sem, aes(x=Group, y=AUC, fill=Group)) + 
  geom_bar(stat="summary", color="black") + 
  geom_errorbar(data=auc_sem, aes(ymin=AUC-sem, ymax=AUC+sem), width=0.25) + 
  geom_jitter(data=auc, aes(y=AUC, x=Group), size=0.5, width=0.3, alpha=0.7) +
  theme_pubr(base_size=11) +
  NoLegend() + 
  labs(x="", y="Plasma Glucose AUC") + 
  ylim(0,50000) + 
  scale_fill_manual(values=wccols) +
  theme(aspect.ratio = 1.5, axis.text.x = element_text(angle=45, hjust=1, vjust=0.98))

#T.tests with Bonferroni correction for multiple comparisons
compare_means(AUC ~ Group, data = auc, method="t.test", p.adjust.method = "bonferroni")

```

## Figure 1G

```{r Fig1G, fig.height=3, fig.width=4, message=FALSE, warning=FALSE}
# Without stats (added in Ppt)
ggplot(subset(tissuemass,Tissue=="pgAT"), aes(x=Group, y=Mass, fill=Group)) + 
  geom_bar(stat="summary", color="black", width=0.8) + 
  geom_errorbar(data=subset(tissuemass_sem, Tissue=="pgAT"), aes(ymin=Mass-sem, ymax=Mass+sem), width=0.25) + 
  geom_jitter(size=0.5, width=0.3, alpha=0.7) + 
  theme_pubr(base_size=11) +
  NoLegend() + 
  labs(x="", y="eAT Mass (g)") + 
  scale_fill_manual(values=wccols) +
  theme(aspect.ratio = 1.5, axis.text.x = element_text(angle=45, hjust=1, vjust=0.98)) 

ggplot(subset(tissuemass,Tissue=="sAT"), aes(x=Group, y=Mass, fill=Group)) + 
  geom_bar(stat="summary", color="black", width=0.8) + 
  geom_errorbar(data=subset(tissuemass_sem, Tissue=="sAT"), aes(ymin=Mass-sem, ymax=Mass+sem), width=0.25) +  
  geom_jitter(size=0.5, width=0.3, alpha=0.7) + 
  theme_pubr(base_size=11) +
  NoLegend() + 
  labs(x="", y="sAT Mass (g)") + 
  scale_fill_manual(values=wccols) +
  theme(aspect.ratio = 1.5, axis.text.x = element_text(angle=45, hjust=1, vjust=0.98)) 

ggplot(subset(tissuemass,Tissue=="Liver"), aes(x=Group, y=Mass, fill=Group)) + 
  geom_bar(stat="summary", color="black", width=0.8) + 
  geom_errorbar(data=subset(tissuemass_sem, Tissue=="Liver"), aes(ymin=Mass-sem, ymax=Mass+sem), width=0.25) + 
  geom_jitter(size=0.5, width=0.3, alpha=0.7) + 
  theme_pubr(base_size=11) +
  NoLegend() + 
  labs(x="", y="Liver Mass (g)") + 
  scale_fill_manual(values=wccols) +
  theme(aspect.ratio = 1.5, axis.text.x = element_text(angle=45, hjust=1, vjust=0.98)) 
  

# For stats
## eAT/pgAT
compare_means(Mass ~ Group, data = subset(tissuemass,Tissue=="pgAT"), method="t.test", p.adjust.method = "bonferroni")

## sAT
compare_means(Mass ~ Group, data = subset(tissuemass,Tissue=="sAT"), method="t.test", p.adjust.method = "bonferroni")

## Liver
compare_means(Mass ~ Group, data = subset(tissuemass,Tissue=="Liver"), method="t.test", p.adjust.method = "bonferroni")
```

## Figure 1H

Immunofluorescence for Perilipin-1, no analysis performed in R.

## Figure 1I
For manuscript: I did not calculate stats in the published data because the distribution is more biologically meaningful. However, there is a statistical difference in adipocyte (or at least, lipid droplet) size between samples. This code reproduces Figure1 panel I, but also provides statistics and other visualization methods for any future reference. 

Note: We subset based on the diameter knowing that adipocytes <20 or >150 are probably artifacts (dead CLS, immune cells, bubbles in the coverslip media).
```{r Figisetup}
adipocount <- read.csv("../Inputs/Fig1/MC74_AdipocyteCount_Skeletonize.csv")
adipocount$Group <- factor(adipocount$Group, levels = c("Lean","Obese","WL","WC"))
```

```{r Fig1i, fig.width=5, fig.height=4}
#T.test with Bonferroni correction for multiple comparisons
## With size thresholds
compare_means(Diameter ~ Group, data = subset(adipocount, Diameter<150 & Diameter>20), method="t.test", p.adjust.method = "bonferroni")
## Without adjusting for size thresholds
compare_means(Diameter ~ Group, data = adipocount, method="t.test", p.adjust.method = "bonferroni")

#Plot distribution with a box and whisker plot
ggboxplot(d=subset(adipocount, Diameter<150 & Diameter>20), 
          x="Group", 
          y="Diameter",  
          fill="Group", 
          add = "mean_se")  +
    theme_classic() +
    scale_fill_manual(values=wccols) +
    theme(axis.text.x=element_text(face="bold", size=10)) + 
    labs(x="", y="") +
    theme(axis.text.x = element_blank(), axis.ticks = element_blank()) +
    NoLegend() 

#Plot distribution with a violin plot
ggplot(subset(adipocount, Diameter<150 & Diameter>20), aes(x=Group, y=Diameter, fill=Group)) + 
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), 
              scale = "count", 
              trim = FALSE, 
              adjust = 1) +
  labs(x="Group", y="Estimated Diameter (um)") + 
  scale_fill_manual(values=wccols) + 
  theme_classic()

#Plot a density distribution
ggplot(subset(adipocount, Diameter<150 & Diameter>10), aes(Diameter)) + 
  geom_histogram(aes(y=..density.., fill=Group),stat="bin", binwidth=5,position="identity", alpha=0.4) + 
  theme_classic() + 
  scale_fill_manual(values=wccols) + 
  geom_density(aes(color=Group)) + 
  scale_color_manual(values=wccols) 

#Ridgeplot colored by adipocyte size
ggplot(subset(adipocount, Diameter<150 & Diameter>10), aes(y=Group, x=Diameter, fill=stat(x))) + 
  geom_density_ridges_gradient(scale = 3, 
                               size= 0.2, 
                               rel_min_height=0.01,
                               quantile_lines=TRUE,
                               quantiles=0.5) + 
  theme_classic() + 
  scale_fill_viridis(name="Diameter", 
                     option="C",
                     limits=c(0,150)) +
  NoLegend()

#Ridgeplot colored by group with median plotted for all cells (no downsampling)
ggplot(subset(adipocount, Diameter<150 & Diameter>20), aes(y=Group, x=Diameter, fill=Group, alpha=0.8)) + 
  geom_density_ridges2(scale = 3,
                       size= 0.2, 
                       rel_min_height=0.01,
                       quantile_lines=TRUE,
                       quantiles=0.5,
                       vline_size=0.5) + 
  theme_classic() + 
  scale_fill_manual(values=wccols) +
  NoLegend()

#Downsampled ridgeplot with rain jitter of samples showing distribution for a random 20000 cells (~5000 per group)
ggplot(subset(adipocount[sample(1:nrow(adipocount), 20000),], Diameter<150 & Diameter>20), aes(y=Group, x=Diameter, fill=Group, alpha=0.9)) + 
  geom_density_ridges2(aes(point_color=Group, vline_color=Group),
                       scale = 3,
                       size= 0.2, 
                       rel_min_height=0.01,
                       jittered_points=TRUE,
                       quantile_lines=TRUE,
                       quantiles=0.5,
                       vline_size=0.75,
                       point_size=0.01,
                       point_alpha=1,
                       position="points_jitter") + 
  labs(x=expression("Lipid Droplet Diameter" ~(μm^2)),y="") +
  theme_classic(base_size = 16) + 
  scale_fill_manual(values=wccols) +
  scale_fill_manual(aesthetics=c("point_color", "vline_color"),values=wccols) +
  scale_color_manual(values=wccols) +
  NoLegend() +
  theme(panel.grid.major = element_line(color="lightgrey"))
```

#Session Info
```{r}
sessionInfo()
```

